---
title: "Assignment"
output:
  html_document:
    keep_md: yes
    toc: yes
---

Prepare for model building
================================
First download the data.
```{r}
library(caret)
train<-read.csv("./training.csv",header=T)
testing<-read.csv("./testing.csv",header=T)
training<-train[,c(6:11,37:49,60:68,84:86,102,113:124,140,151:160)]
```
The original dataset training has 19622 obervations and 160 variables including the one we are predicting for----variable "classe". We filter the first five colunms and the colunms with missing data to create new dataset "traning".

```{r}
table(training$classe)
```
classe is a factor varibale, and there are five levels of classe.


Model building
=================
#classification tree
```{r}
modfit<-train(classe~.,data=training,method="rpart")#12min
modfit$finalModel
```
Above is the final model.And we can plot the tree below.

```{r plot1}
library(rattle)
fancyRpartPlot(modfit$finalModel,main="Classification Tree",sub="")
```

```{r}
modfit$results[1,]
```
The accuracy of the final model is 0.55 on training data,and the kappa value equals 0.42.

```{r plot2}
library(ggplot2)
qplot(roll_belt,pitch_forearm,colour=classe,data=training)
```




